Two Decades of Smalltalk VM Development

### 2018-08-17 paper.tex
Fixed two typos in sec 5.2

>>>>

Analysing the question is easy in our context.  This analysis took about an hour to perform, including writing an iterator over send sites, and then implementing the eager promotion to open PICs.  Somewhat similar analyses one of the authors performed on the second generation Deutsch Schiffman VM \cite{EfficientST80} , which is written entirely in C, when adding the same PIC scheme took several days, having to be written statically and tested with a traditional edit-compile-debug cycle. The productivity difference is extreme.
